
\documentclass{resume}

\newcommand{\PHIL}[0]{\DepartmentTitle{Philosophy Department}}
\newcommand{\COMP}[0]{\DepartmentTitle{Computer Science Department}}
\newcommand{\CAAM}[0]{\DepartmentTitle{Applied Math Department}}
\newcommand{\other}[0]{\DepartmentTitle{other departments}}
\newcommand{\IB}[0]{\DepartmentTitle{IB Coursework}{}}
\newcommand{\AP}[0]{\DepartmentTitle{AP Coursework}{}}

\newcommand{\Southridge}[0]{\UniversityTitle{Southridge High School}{}}
\newcommand{\Rice}[0]{\UniversityTitle{Rice University}{}}
\newcommand{\Brandeis}[0]{\UniversityTitle{Brandeis University}{}}
\newcommand{\UCR}[0]{\UniversityTitle{University of California at Riverside}{}}

\newcommand{\ToPresent}[0]{\textbf{to present}}

\newcommand{\maru}[0]{Maru{\v s}i{\' c}}
\newcommand{\beri}[0]{Berislav \maru}
\newcommand{\jen}[0]{Jennifer \maru}
\newcommand{\jozef}[0]{Jozef M\"{u}ller}





\name{Nicholas Hanson-Holtry}

\iftoggle{cv}{
  \title{%
  \texttt{\{nicholas.hanson.holtry@gmail.com\}}\\
  \texttt{\{http://www.nicholashh.com\}}\\~\\
  % \texttt{\{503.360.3148\}}}
  pronouns:~``they/them/their''
  }
}{
  \title{%
  \texttt{\{nicholas.hanson.holtry@gmail.com\}}\\
  \texttt{\{www.nicholashh.com\}}\\
  % \texttt{\{503.360.3148\}}}
  ``they/them/their''
  }
}

\begin{document}

% \begin{center}
% applying to: Philosophy PhD
% \end{center}





\begin{rSection}{Education}

  % \begin{rSubSection}
  \EventWithSubtitle
  % {??? \normalfont University}
  % {\normalfont University of California at Riverside}
  {\normalfont University of California at Riverside}
  {Los Angeles, California}
  % {\bf Doctor \normalfont of Philosophy in \bf Philosophy}
  % {\bf Ph.D \normalfont in \bf Philosophy}
  {\bf PhD in Philosophy}
  % {Philosophy MA}
  % {Fall 2017 \ToPresent}%
  {Fall 2019 \ToPresent}%
  % \iftoggle{cv}{
  %   \item ?
  % }{
  %   \item ?
  % }
  % \end{rSubSection}

  \iftoggle{cv}{
    \begin{rSubSection}
    % \EventWithSubtitle
    % {Brandeis \normalfont University}
    {\normalfont Brandeis University}
    {Boston, Massachusetts}
    % {\bf Master \normalfont of Arts in \bf Philosophy}
    % {\bf M.A. \normalfont in \bf Philosophy}
    {\bf MA in Philosophy}
    {Fall 2017 to Spring 2019}%
    \iftoggle{cv}{
      \item Thesis:~``Reasoning First Rationality''
      % \item Advisors:~Dr.~Berislav Maru{\v s}i{\' c}, Dr.~Eli Hirsch
      \item Advisors:~\beri, Eli Hirsch
      % \item Philosophy GPA:~\tab{$4.00/4.00$}
      % \item Overall GPA:~\tab{$3.97/4.00$}
    }{
      \item GPA:~$3.97/4.00$
    }
    \end{rSubSection}
  }{}

  % \iftoggle{cv}{
  %   \begin{rSubSection}
  % }{
    \EventWithSubtitle
  % }
  % {Rice \normalfont University~(SRC)}
  {\normalfont Rice University~(SRC)}
  {Houston, Texas}
  % {\bf Bachelor \normalfont of Science in \bf Computer Science}
  % {\bf B.S. \normalfont in \bf Computer Science}
  {\bf BS in Computer Science}
  {Fall 2012 to Spring 2016}%
  % \iftoggle{cv}{
  %   \item Comp Sci GPA:~\tab{$3.68/4.00$}
  %   \item Overall GPA:~\tab{$3.61/4.00$}
  % }{%
  %   % \item GPA:~$3.61/4.00$
  % }
  % \iftoggle{cv}{
  %   \end{rSubSection}
  % }{}%

  \iftoggle{cv}{

    % \begin{rSubSection}
    \EventWithSubtitle
    {\normalfont Southridge High School}
    {Portland, Oregon}
    % {International Baccalaureate Diploma}
    % {IB Diploma}
    % {IB Diploma~($37/45$)}
    {International Baccalaureate Diploma}
    {Fall 2010 to Spring 2012}%
    % {Fall 2008 to Spring 2012}%
    % \item GPA:~$3.97/4.00$
    % \end{rSubSection}

  %   \EventWithSubtitle
  %   {\normalfont Summa South Middle School}
  %   {Fall 2005 to Spring 2008}
  %   {}
  %   {}

  %   \EventWithSubtitle
  %   {\normalfont Raleigh Hills Elementary School}
  %   {Fall 1999 to Spring 2005}
  %   {}
  %   {}

  }{}





\end{rSection}





% \iftoggle{cv}{\pagebreak}{}

\iftoggle{cv}{
  \begin{rSection}{Teaching Experience}

    \iftoggle{cv}{

      \UCR

        \PHIL

          \begin{UnivDeptItem}
          {Applied Ethics}
          {Fall 2020}
          {with Dr.~Patrick Londen}
          {}%
          \item Taught 3x20 students for 50 mins once per week, graded papers, etc.
          \end{UnivDeptItem}

      \Brandeis

        \PHIL

          \begin{UnivDeptItem}
          {Biomedical Ethics}
          {Spring 2019}
          {with Dr.~Eli Hirsch}
          {}%
          \item Held office hours, graded assignments+exams, etc.
          \end{UnivDeptItem}

  \iftoggle{cv}{\pagebreak}{}

          \begin{UnivDeptItem}
          {Neuroethics}
          {Fall 2018}
          {with Dr.~Brendan Cline}
          {}%
          \item Taught class when the professor was unavailable.
          \item Held office hours, graded assignments+exams, etc.
          \end{UnivDeptItem}

          \begin{UnivDeptItem}
          {Aesthetics}
          {Spring 2018}
          {with Dr.~Andreas Teuber}
          {}%
          \item Held office hours, graded assignments+exams, etc.
          \end{UnivDeptItem}

    }{}

    \iftoggle{cv}{
      \vspace{1ex}
      \begin{rSubSection}
      {\underline{Varsity Tutors}}
    }{
      \EventWithSubtitle
      {Varsity Tutors}
    }
    {online + Miami, Florida}
    {Contractor / Certified Tutor}
    {Fall 2016 to Summer 2017}%
    \iftoggle{cv}{
      \item Tutored high school and undergraduate students in a variety\\
      of subjects, ranging from writing to coding to SAT test prep.
      \end{rSubSection}
    }{}

    \iftoggle{cv}{

      \Rice

        \CAAM

          \begin{UnivDeptItem}
          {Introduction to Computational Engineering}
          {Spring 2013 to Spring 2016}
          {with Dr.~Steven Cox, Dr.~Franklin Kenter, and Dr.~Illya Hicks}
          {}%
          \item Taught class when the professor was unavailable.
          \item Taught 1 recitation of $\sim$15 students $\sim$1 time/week.
          \item Created and assigned 2 original homework assignments.
          \item Held office hours, graded assignments+exams, etc.
          \end{UnivDeptItem}

        \COMP

          \begin{UnivDeptItem}
          {Principles of Parallel Programming}
          {Spring 2015, Spring 2016}
          {with Dr.~Vivek Sarkar and Dr.~Eric Allen}
          {}%
          \item Held office hours, graded assignments+exams, etc.
          \end{UnivDeptItem}

          \begin{UnivDeptItem}
          {Reasoning About Algorithms}
          {Fall 2015}
          {with Dr.~Swarat Chaudhuri}
          {}%
          \item Taught 1 recitation of $\sim$10 students $\sim$2 times/week.
          \item Held office hours, graded assignments+exams, etc.
          \end{UnivDeptItem}

          \begin{UnivDeptItem}
          {Computational Thinking}
          {Fall 2013, Fall 2014}
          {with Dr.~Scott Rixner}
          {}%
          \item Taught 1 recitation of $\sim$15 students $\sim$3 times/week.
          \item Held office hours, graded assignments+exams, etc.
          \end{UnivDeptItem}

    }{

      \EventWithSubtitle
      {Rice University}
      {Houston, Texas}
      {Teaching Assistant / Lecturer}
      {Spring 2013 to Spring 2016}%

    }

  \end{rSection}

}{

}





\iftoggle{cv}{}{

  \begin{rSection}{Recent Personal Projects}

    \Event{\texttt{\{https://nicholashh.github.io/phil-ranker\}}}{Fall 2018}\\
    \Event{\texttt{\{https://github.com/nicholashh/arch/blob/master/note\}}}{Summer 2019}

  \end{rSection}

}





\iftoggle{cv}{\pagebreak}{}
% \begin{rSection}{Academic Research Experience}
\begin{rSection}{Academic Research}

  \iftoggle{cv}{
    \Rice
    \PHIL
  }{
    \begin{rSubSection}
    {\normalfont Rice University}
    {}
    {}
    {}
  }

  \iftoggle{cv}{
    \begin{UnivDeptItem}{Dr.~Timothy Schroeder}{Summer 2016 to Summer 2017}{}{}
    \item Prototyped an open-source website (and accompanying database)\\
    of assertions and arguments made by professional philosophers.
    \end{UnivDeptItem}
  }{
    \item {\bf Dr.~Timothy Schroeder}
    (philosophical database prototype)
    \hfill Summer 2016 to Summer 2017%
  }

% \iftoggle{cv}{\pagebreak}{}

  \iftoggle{cv}{
    \COMP
  }

  \iftoggle{cv}{
    \begin{UnivDeptItem}{Dr.~Swarat Chaudhuri}{Summer 2015 to Fall 2015}{}{}
    \item Investigated a computational definition of ethical fairness.
    \item Investigated formal methods assurances of fairness.
    \item Investigated post hoc verification of fairness.
    \end{UnivDeptItem}
  }{
    \item {\bf Dr.~Swarat Chaudhuri}
    (program verification + fairness)
    \hfill Summer 2015 to Fall 2015%
  }

  \iftoggle{cv}{
    \begin{UnivDeptItem}{Dr.~Vivek Sarkar}{Spring 2015}{}{}
    \item Investigated optimal parallel \texttt{map} implementations.
    \item Contributed to the parallel computing suite Habanero Java.
    \end{UnivDeptItem}
  }{
    \item {\bf Dr.~Vivek Sarkar}
    (parallel computation suite development)
    \hfill Spring 2015%
  }

  \iftoggle{cv}{
    \begin{UnivDeptItem}{Dr.~Luay Nakhleh}{Summer 2014}{}{}
    \item Investigated introgressed genes in the \emph{mus musculus} genome.
    \item Applied clustering algorithms to protein-protein interaction\\
    network data to confirm previously identified genome patterns.
    \item Identified previously unknown introgressed gene candidates.
    \end{UnivDeptItem}
  }{
    \item {\bf Dr.~Luay Nakhleh}
    (bioinformatics + graph theory)
    \hfill Summer 2014%
  }

  \iftoggle{cv}{
    \begin{UnivDeptItem}{Dr.~Devika Subramanian}{Spring 2013}{}{}
    \item Applied machine learning algorithms to medical data.
    \end{UnivDeptItem}
  }{
    \item {\bf Dr.~Devika Subramanian}
    (machine learning + medicine)
    \hfill Spring 2013%
  }

  \iftoggle{cv}{}{
    \end{rSubSection}
  }

\end{rSection}

\iftoggle{cv}{

  \begin{rSection}{Coursework / Transcript}

    \UCR

      \PHIL

        \BeginDeptEvents
        % \Event{Moral Address~\tab\tab\tab\tab{Coleen Macnamara}\tab{\texttt{?}}}{Winter 2021}\\
        \Event{Forgiveness \& Its Limits~\tab\tab\tab{Myisha Cherry}\tab{\texttt{A+}}}{Fall 2020}\\
        \Event{Kant --- Pure Reason~\tab\tab\tab{Alexandra Newton}\tab{\texttt{A-}}}{Fall 2020}\\
        \Event{Groups Of People~\tab\tab\tab\tab{Adam Harmer}\tab{audit}}{Fall 2020}\\
        \Event{Proseminar --- Scanlon, Korsgaard~\tab{Andrews Reath}\tab{\texttt{A}}}{Spring 2020}\\
        \Event{Meta-Logic~\tab\tab\tab\tab\tab{Erich Reck}\tab\tab{\texttt{A+}}}{Spring 2020}\\
        \Event{Hyman~\tab\tab\tab\tab\tab{Kim Frost}\tab\tab{\texttt{A}}}{Spring 2020}\\
        \Event{Aristotle --- Nicomachean Ethics~\tab\tab{\jozef}\tab\tab{\texttt{?}}}{Spring 2020}\\
        \Event{Nietzsche --- Naturalism~\tab\tab\tab{Maude Clark}\tab\tab{audit}}{Spring 2020}\\
        \Event{Motivation~\tab\tab\tab\tab\tab{Agnieszka Jaworska}\tab{audit}}{Spring 2020}\\
        \Event{Proseminar --- Gettierology~\tab\tab{Peter Graham}\tab{\texttt{A}}}{Winter 2020}\\
        \Event{Brandom's Hegel~\tab\tab\tab\tab{Pierre Keller}\tab\tab{\texttt{A}}}{Winter 2020}\\
        \Event{Frege~\tab\tab\tab\tab\tab\tab{Erich Reck}\tab\tab{\texttt{A-}}}{Winter 2020}\\
        \Event{Moral Psychology --- Gratitude~\tab\tab{Coleen Macnamara}\tab{audit}}{Winter 2020}\\
        \Event{Moral Constitutivism --- Objections~\tab{Luca Ferrero}\tab\tab{\texttt{A}}}{Winter 2020}\\
        \Event{Moral Constitutivism --- Kant~\tab\tab{Michael Nelson}\tab{\texttt{A}}}{Fall 2019}\\
        \Event{Proseminar --- Descartes, Leibniz~\tab\tab{Adam Harmer}\tab{\texttt{A}}}{Fall 2019}\\
        \Event{Dynamic Structuralism~\tab\tab\tab{Pierre Keller}\tab\tab{\texttt{A-}}}{Fall 2019}\\
        \Event{The Aspect Of Eternity --- Nagel~\tab\tab{Howard Wettstein}\tab{\texttt{A}}}{Fall 2019}\\
        \Event{Moral Psychology --- Negative Affect~\tab{Myisha Cherry}\tab{audit}}{Fall 2019}
        \EndDeptEvents

    \Brandeis

      \PHIL

        \BeginDeptEvents
        \Event{Mind --- Burge, Millikan (\emph{Seminar})\tab{Jerry Samet}\tab\tab{\texttt{A}}}{Spring 2019}\\
        \Event{Language~\tab\tab\tab\tab\tab{Eli Hirsch}\tab\tab{\texttt{A}}}{Spring 2019}\\
        \Event{Explanation \& Causation~\tab\tab\tab{\jen}\tab{\texttt{A+}}}{Spring 2019}\\
        \Event{Aristotle~\tab\tab\tab\tab\tab{Palle Yourgrau}\tab{\texttt{A}}}{Spring 2019}\\
        \Event{Biomedical Ethics~\tab\tab\tab\tab{Eli Hirsch}\tab\tab{audit}}{Spring 2019}\\
        \Event{Rationality (\emph{Independent Study})\tab\tab\beri\tab{\texttt{A}}}{Fall 2018}\\
        \Event{Action~\tab\tab\tab\tab\tab\beri\tab{\texttt{A}}}{Fall 2018}\\
        \Event{Kant --- Pure Reason~\tab\tab\tab{Kathleen Moran}\tab{\texttt{A+}}}{Fall 2018}\\
        \Event{Metaethics --- Parfit~\tab\tab\tab{Eli Hirsch}\tab\tab{\texttt{A}}}{Fall 2018}\\
        \Event{Personal Identity~\tab\tab\tab\tab{Eli Hirsch}\tab\tab{audit}}{Fall 2018}\\
        \Event{Self-Knowledge~\tab\tab\tab\tab\beri\tab{audit}}{Fall 2018}\\
        \Event{Neuroethics~\tab\tab\tab\tab\tab{Brendan Cline}\tab{audit}}{Fall 2018}\\
        \Event{Hume --- Human Nature~\tab\tab\tab{\jen}\tab{audit}}{Fall 2018}\\
        \Event{External World Skepticism (\emph{Seminar})\tab\beri\tab{\texttt{A}}}{Spring 2018}\\
        \Event{Space \& Time~\tab\tab\tab\tab{Eli Hirsch}\tab\tab{\texttt{A}}}{Spring 2018}\\
        \Event{Mathematical Logic~\tab\tab\tab\tab{\jen}\tab{\texttt{A}}}{Spring 2018}\\
        \Event{Wittgenstein --- Investigations~\tab\tab{Eli Hirsch}\tab\tab{\texttt{A}}}{Spring 2018}\\
        \Event{Mind~\tab\tab\tab\tab\tab\tab{Jerry Samet}\tab\tab{audit}}{Spring 2018}\\
        \Event{The Idea Of God~\tab\tab\tab\tab{Palle Yourgrau}\tab{audit}}{Spring 2018}\\
        \Event{Descartes, Spinoza, \& Leibniz~\tab\tab{\jen}\tab{audit}}{Spring 2018}\\
        \Event{Proseminar (\emph{Seminar})\tab\tab\tab{Andreas Teuber}\tab{\texttt{A}}}{Fall 2017}\\
        \Event{Ethics \& Emotions~\tab\tab\tab\tab{Kathleen Moran}\tab{\texttt{A}}}{Fall 2017}\\
        \Event{Hegel --- Phenomenology Of Spirit~\tab{Eugene Sheppard}\tab{\texttt{A}}}{Fall 2017}\\
        \Event{Existentialism --- Sartre, Beauvoir~\tab\beri\tab{\texttt{A}}}{Fall 2017}
        \EndDeptEvents

      \other

        \BeginDeptEvents
        \Event{Buddhism~\tab\tab\tab\tab\tab\tab\texttt{RELI}\tab\texttt{~YF}\tab{audit}}{Spring 2019}\\
        \Event{History Of Photography~\tab\tab\tab\tab\texttt{ARTS}\tab\texttt{PK}\tab{audit}}{Spring 2019}\\
        \Event{Marx, Nietzsche, \& \nth{20}c Radicalism~\tab\tab\texttt{POLI}\tab\texttt{~BY}\tab{\texttt{A-}}}{Fall 2017}
        \EndDeptEvents

    \Rice

      \PHIL

        \BeginDeptEvents
        \Event{Continental Philosophy~\tab\tab\tab{Steven Crowell}\tab{\texttt{A-}}}{Spring 2016}\\
        \Event{History Of Philosophy~\tab\tab\tab{Charles Siewert}\tab{\texttt{B+}}}{Fall 2013}\\
        \Event{Social \& Political Philosophy~\tab\tab{George Sher}\tab\tab{\texttt{A-}}}{Spring 2013}
        \EndDeptEvents

      \COMP

        \BeginDeptEvents
        \Event{Advanced Topics In Object-Oriented Design~\tab\tab\texttt{~SW}\tab{\texttt{B}}}{Spring 2016}\\
        \Event{Advanced Computer Game Creation~\tab\tab\tab\texttt{~JW}\tab{\texttt{B+}}}{Spring 2016}\\
        \Event{Tools \& Models For Data Science~\tab\tab\tab\tab\texttt{~CJ}\tab{\texttt{A}}}{Fall 2015}\\
        \Event{Functional Programming~\tab\tab\tab\tab\tab\texttt{~EA}\tab{\texttt{A}}}{Fall 2015}\\
        \Event{Operating Systems \& Concurrent Programing~\tab\tab\texttt{~DJ}\tab{\texttt{B}}}{Spring 2015}\\
        \Event{Introduction To Computer Security~\tab\tab\tab\texttt{~DW}\tab{\texttt{A+}}}{Spring 2015}\\
        \Event{Introduction To Object-Oriented Design~\tab\tab\tab\texttt{~SW}\tab{\texttt{A}}}{Fall 2014}\\
        \Event{Reasoning About Algorithms~\tab\tab\tab\tab\texttt{~SC}\tab{\texttt{A}}}{Fall 2014}\\
        \Event{Compiler Construction~\tab\tab\tab\tab\tab\texttt{~KC}\tab{\texttt{A-}}}{Fall 2014}\\
        \Event{Principles Of Parallel Programming~\tab\tab\tab\texttt{~VS}\tab{\texttt{B}}}{Spring 2014}\\
        \Event{Introduction To Computer Systems~\tab\tab\tab\texttt{~AC}\tab{\texttt{A-}}}{Spring 2014}\\
        \Event{Introduction To Program Design~\tab\tab\tab\tab\texttt{~CJ}\tab{\texttt{A}}}{Fall 2013}\\
        \Event{Algorithmic Thinking~\tab\tab\tab\tab\tab\texttt{~LN}\tab{\texttt{A-}}}{Spring 2013}\\
        \Event{Computational Thinking~\tab\tab\tab\tab\tab\texttt{~DS}\tab{\texttt{A}}}{Fall 2012}
        \EndDeptEvents

% \iftoggle{cv}{\pagebreak}{}

      \other

        \BeginDeptEvents
        \Event{Linear Algebra~\tab\tab\tab\tab\tab\texttt{CAAM}\tab\texttt{~ME}\tab{\texttt{A}}}{Fall 2013}\\
        \Event{Multivariable Calculus~\tab\tab\tab\tab\texttt{MATH}\tab\texttt{~NK}\tab{\texttt{A-}}}{Spring 2013}\\
        \Event{Fundamentals Of Computer Engineering~\tab\tab\texttt{ELEC}\tab\texttt{~JC}\tab{\texttt{B-}}}{Spring 2013}\\
        \Event{Ordinary Differential Equations~\tab\tab\tab\texttt{MATH}\tab\texttt{~SB}\tab{\texttt{B-}}}{Fall 2012}\\
        \Event{Introduction To Computational Engineering~\tab\texttt{CAAM}\tab\texttt{~SC}\tab{\texttt{A+}}}{Fall 2012}
        \EndDeptEvents

    \Southridge

      \IB

        \BeginDeptEvents
        \Event{\texttt{TOTAL}~\tab\tab\tab\tab\tab\tab\tab\tab\tab{\texttt{37/45}}}{}\\
        \Event{\texttt{(HL)} English~\tab\tab\tab\tab\tab\tab\tab\tab{\texttt{5(/7)}}}{2011-2012}\\
        \Event{\texttt{(SL)} Spanish~\tab\tab\tab\tab\tab\tab\tab{\texttt{6}}}{2011}\\
        \Event{\texttt{(SL)} Psychology~\tab\tab\tab\tab\tab\tab\tab{\texttt{5}}}{2011}\\
        \Event{\texttt{(SL)} Chemistry~\tab\tab\tab\tab\tab\tab\tab{audit}}{2010}\\
        \Event{\texttt{(HL)} Physics~\tab\tab\tab\tab\tab\tab\tab\tab{\texttt{6}}}{2011-2012}\\
        \Event{\texttt{(HL)} Math~\tab\tab\tab\tab\tab\tab\tab\tab{\texttt{6}}}{2011-2012}\\
        \Event{\texttt{(SL)} Environmental Systems \& Societies~\tab\tab\tab{\texttt{6}}}{2012}\\
        \Event{Extended Essay \texttt{(English)}~\tab\tab\tab\tab\tab{\texttt{A}}}{2012}\\
        \Event{Theory of Knowledge~\tab\tab\tab\tab\tab\tab{\texttt{B}}}{2012}
        \EndDeptEvents

      \AP

        \BeginDeptEvents
        \Event{US History~\tab\tab\tab\tab\tab\tab\tab\tab{\texttt{4(/5)}}}{2010}\\
        \Event{Statistics~\tab\tab\tab\tab\tab\tab\tab\tab{\texttt{5}}}{2010}
        \EndDeptEvents

  \end{rSection}

}{}





% \begin{rSection}{Professional Work History}
\begin{rSection}{Professional Work}

  \iftoggle{cv}{
    \begin{rSubSection}
    {Shepherd Artisan Coffee}
    {Miami, Florida}
    {Barista}
    {Fall 2016}%
    \item Learned to make cappuccinos.
    \end{rSubSection}
  }

  \iftoggle{cv}{
    \begin{rSubSection}
  }{
    \EventWithSubtitle
  }
  {Jones McClure Publishing}
  {Houston, Texas}
  {Software Development Intern}
  {Summer 2013}%
  \iftoggle{cv}{
    \item Prototyped a mobile version of the existing desktop website.
    \end{rSubSection}
  }{}

  \iftoggle{cv}{
    \begin{rSubSection}
    {Tualatin Hills Park \& Recreation District}
    {Portland, Oregon}
    {Swim Coach / Swim Instructor / Lifeguard}
    {Summer 2010 to Summer 2012}%
    \item Coached the swim team; taught swim lessons; guarded lives.
    \end{rSubSection}
  }

\end{rSection}





% \iftoggle{cv}{\pagebreak}{}
% \begin{rSection}{Volunteer Work / Extracurricular Activities}
\iftoggle{cv}{%
\begin{rSection}{Volunteer Work / Extracurriculars}%
}{%
\begin{rSection}{Volunteer Work}%
}%

  \iftoggle{cv}{
    \begin{rSubSection}
  }{
    \EventWithSubtitle
  }
  {The OpenDota Project \normalfont \texttt{\{https://www.opendota.com\}}}
  {online}
  {Co-Founder / DevOps / Public Relations}
  % {Co-Founder / DevOps / Public Relations / ``Bus Guy''}
  {Fall 2014 \ToPresent}%
  \iftoggle{cv}{
    \item Writes and edits blog posts, as needed.
    \item Trained in site maintenance and administration.
    \item Involved in initial planning of site.
    \end{rSubSection}
  }{}

  \iftoggle{cv}{
    \begin{rSubSection}
  }{
    \EventWithSubtitle
  }
  {Rice University Queer Resource Center}
  {Houston, Texas}
  {Co-Founder / First President}
  {Fall 2014 to Spring 2016}%
  \iftoggle{cv}{
    \item Wrote a successful funding proposal to the Rice Undergraduate Student\\
    Association and was approved by the student body to receive \$5,000.
    \item Facilitated discussion among $\sim$20 disparate committees $\sim$2 times/month.
    \item Headed the Sexual Assault Committee, co-headed Ally Training Committee,\\
    worked to hire a part-time staff person to support the Center, investigated\\
    founding a queer support group, and created the Center's website.
    \end{rSubSection}
  }{}

  \iftoggle{cv}{

    % TODO:~make a conferences section (after going to another conference)
    \begin{rSubSection}
    {Out for Undergrad Technology Conference}
    {San Francisco, California}
    {Student Participant (selected by admissions committee)}
    {25-27 September 2015}%
    \item Attended the conference (which is dedicated to helping \\ 
    high-achieving LGBTQ+ undergraduates in technological\\
    STEM fields reach their full potential in their careers).
    \end{rSubSection}

    \begin{rSubSection}
    {Sid Richardson College Academic Fellows Program}
    {Houston, Texas}
    {Academic Fellow (Computer Science)}
    {Fall 2014 to Spring 2016}%
    \item Held ``open office hours'' in which any student in any class\\
    could get help on any topic (related to computer science).
    \item Taught various ``workshops'' (related to computer science).
    \item Oversaw computer science fellowship within the college.
    \end{rSubSection}

    \begin{rSubSection}
    {Rice University Peer Academic Advisor Program}
    {Houston, Texas}
    {Academic Advisor}
    {Spring 2013 to Spring 2016}%
    \item Academically advised students within the college.
    \end{rSubSection}

    \begin{rSubSection}
    {Rice University Student Ambassador Program}
    {Houston, Texas}
    {Student Ambassador}
    {Spring 2013 to Spring 2016}%
    \item Gave tours of the university to ``distinguished'' guests.
    \end{rSubSection}

    \EventWithSubtitle
    {Southridge High School Speech and Debate Team}
    {Portland, Oregon}
    {Capitan of Debate}
    {2011-2012}%

    \EventWithSubtitle
    {Southridge High School Swim Team}
    {Portland, Oregon}
    {Co-Capitan}
    {2011-2012}%

  }{}

\end{rSection}





\iftoggle{cv}{

  % \iftoggle{cv}{\pagebreak}{}

  \begin{rSection}{Awards / Honors}

  \Event{Max Kade Travel Grant}{Summer 2018}\\
  \Event{Brandeis GSAS Scholarship Grant}{Fall 2017}\\
  \Event{Sid Richardson Athenian Award}{Spring 2016}\\
  \Event{Rice Alumni Pride Award}{Fall 2015}\\
  \Event{Rice President's Honor Roll}{Fall 2014, Fall 2015}\\
  \Event{John and Harriet Millington Scholarship}{Fall 2014, Fall 2015}\\
  \Event{Lon Wilson Service Award}{Spring 2015}\\
  \Event{Genevieve Parkhill Lykes Scholarship}{Fall 2014}\\
  \Event{Bracht-Verlander Scholarship}{Fall 2012}\\
  \Event{National Merit Quarterfinalist}{Spring 2012}\\
  % \Event{AP Scholar with Honor}{Spring 2012}\\
  \Event{National Honor Society}{2011-2012}

  \end{rSection}





%   % \pagebreak

\iftoggle{cv}{\pagebreak}{}

  \begin{rSection}{Standardized Test Scores}

  \begin{rSubSection}{GRE}{November 2015}{}{}
  \item Writing:~\tab\tab\tab{~$4.5/6.0$}\tab\tab{(\nth{80} percentile)}
  \item Verbal:~\tab\tab\tab{$161/170$}\tab\tab{(\nth{87} percentile)}
  \item Quantitative:~\tab\tab{$164/170$}\tab\tab{(\nth{88} percentile)}
  \end{rSubSection}

  \begin{rSubSection}{SAT\hspace{7.85em}$2,300/2,400$\hspace{3.9em}\normalfont(\nth{99} percentile)}{October 2011}{}{}
  \item Writing:~\tab\tab\tab{$760/800$}\tab\tab{(\nth{99} percentile)}
  \item Reading:~\tab\tab\tab{$790/800$}\tab\tab{(\nth{99} percentile)}
  \item Mathematics:~\tab\tab{$750/800$}\tab\tab{(\nth{97} percentile)}
  \end{rSubSection}

  \begin{rSubSection}{ACT\hspace{8.75em}$33/36$\hspace{5.3em}\normalfont(\nth{98} percentile)}{February 2010}{}{}
  \item English:~\tab\tab\tab{\hspace{.5em}$34/36$}\tab\tab\tab{(\nth{98} percentile)}
  \item Reading:~\tab\tab\tab{\hspace{.5em}$29/36$}\tab\tab\tab{(\nth{86} percentile)}
  \item Math:~\tab\tab\tab\tab{\hspace{.5em}$30/36$}\tab\tab\tab{(\nth{94} percentile)}
  \item Science:~\tab\tab\tab{\hspace{.5em}$35/36$}\tab\tab\tab{(\nth{99} percentile)}
  \end{rSubSection}

  \end{rSection}





  \begin{rSection}{Language Proficiency}

  \begin{rSubSection}{\normalfont natural languages}{}{}{}
  \item native/fluent:~English
  \item moderate:~Spanish, American Sign Language
  \item minimal:~Latin
  \end{rSubSection}

  \begin{rSubSection}{\normalfont programming languages}{}{}{}
  \item fluent:~Java, Python, C, JS(/HTML/CSS), SQL, Matlab
  \item moderate:~Bash, Scala, VB.Net
  \end{rSubSection}

  \end{rSection}





  \begin{rSection}{Miscellaneous Information}

  pronouns:~``they/them/their''

  citizenship/nationality:~USA

  Myers-Briggs:~INFJ

  \end{rSection}





}{

  \begin{rSection}{Additional Information}

    % For additional details about the information listed above, as well as information\\
    % about my pertinent coursework, awards and honors, standardized test scores, etc,\\
    % my full CV (\emph{curriculum vitae}) is available online at \{www.nicholashh.com/cv\}.

    My full CV (\emph{curriculum vitae}) is available online at \texttt{\{http://www.nicholashh.com/cv\}}.

  \end{rSection}

}





\end{document}
