
\documentclass{resume}

\newcommand{\Rice}[0]{\UniversityTitle{Rice University}{Houston, Texas}}
\newcommand{\COMP}[0]{\DepartmentTitle{Department of Computer Science}{}}
\newcommand{\CAAM}[0]{\DepartmentTitle{Department of Computational and Applied Mathematics}{}}





\name{Nicholas Hanson-Holtry}

\address{%
nicholashh@rice.edu \\
503.360.3148 \\
6360 Main Street, Houston, Texas, 77005}





\begin{document}

\begin{rSection}{Education}

\begin{rSubSection}{Rice University}{Houston, Texas}
{Bachelor of Science in Computer Science}{expected Spring 2016}
\item GPA: $3.65/4.00$
\end{rSubSection}

\begin{rSubSection}{Southridge High School}{Portland, Oregon}
{International Baccalaureate Diploma}{Spring 2012}
\item GPA: $3.97/4.00$
\end{rSubSection}

\end{rSection}





\begin{rSection}{Research Experience} \iftoggle{cv}{

\Rice

\COMP

\begin{UnivDeptItem}{Dr.~Swarat Chaudhuri}{Summer 2015 to Fall 2015}{}{}
\item Investigated a computational definition of ethical fairness \\
(hiring practices sensitive to personal attributes like race, etc).
\item Investigated formal methods techniques to ensure fairness \\
in probabilistic or machine learning classification algorithms.
\item Investigated post hoc verification of fairness of a classification result.
\end{UnivDeptItem}

\begin{UnivDeptItem}{Dr.~Vivek Sarkar}{Spring 2015}{}{}
\item Investigated tradeoffs among parallel \texttt{map} implementations.
\item Optimized the parallel computing suite Habanero Java.
\end{UnivDeptItem}

\begin{UnivDeptItem}{Dr.~Luay Nakhleh}{Summer 2014}{}{}
\item Researched introgressed genes in the \emph{mus musculus} genome.
\item Applied clustering algorithms to protein-protein interaction \\
network data to confirm previously identified genome patterns.
\item Identified previously unknown introgressed gene candidates \\
to be further investigated by an adjacent group in the lab.
\end{UnivDeptItem}

\begin{UnivDeptItem}{Dr.~Devika Subramanian}{Spring 2013}{}{}
\item Applied machine learning algorithms to medical data.
\end{UnivDeptItem}

}{

\Event{{\bf Dr.~Swarat Chaudhuri}, program verification and fairness}{Summer 2015 to Fall 2015} \\
\Event{{\bf Dr.~Vivek Sarkar}, parallel computing suite development}{Spring 2015} \\
\Event{{\bf Dr.~Luay Nakhleh}, bioinformatics and graph theory}{Summer 2014} \\
\Event{{\bf Dr.~Devika Subramanian}, machine learning and medicine}{Spring 2013}

} \end{rSection}





\iftoggle{cv}{\pagebreak
\begin{rSection}{Teaching Experience}

\Rice

\CAAM

\begin{UnivDeptItem}{Introduction to Computational Engineering}
{Spring 2013 to present}{with Dr.~Steven Cox, Dr.~Franklin Kenter, Dr.~Illya Hicks}{}
\item Taught one hour-long break-out section of the course once \\
per week; each section contained between five and twenty students.
\item Taught the main section of the course when the professor \\
was unavailable; contained approximately one hundred students.
\item Created original course content including two homework assignments.
\item Held weekly office hours and graded assignments and exams.
\end{UnivDeptItem}

\COMP

\begin{UnivDeptItem}{Principles of Parallel Programming}
{Spring 2015, Spring 2016}{with Dr.~Vivek Sarkar, Dr.~Eric Allen}{}
\item Held weekly office hours and graded assignments and exams.
\end{UnivDeptItem}

\begin{UnivDeptItem}{Reasoning About Algorithms}
{Fall 2015}{with Dr.~Swarat Chaudhuri}{}
\item Taught one hour-long tutorial session approximately bi-weekly; \\
each session contained between five and twenty five students.
\item Held weekly office hours and graded assignments and exams.
\end{UnivDeptItem}

\begin{UnivDeptItem}{Computational Thinking}
{Fall 2013, Fall 2014}{with Dr.~Scott Rixner}{}
\item Supervised a flipped-classroom environment; interacted with \\
approximately fifteen students approximately ten times a week.
\item Held weekly office hours and graded assignments and exams.
\end{UnivDeptItem}

\end{rSection} }{}

% {

% \Event{Reasoning About Algorithms, teaching assistant}{Fall 2015} \\
% \Event{Introduction to Computational Engineering, lecturer}{Spring 2013 to present} \\
% \Event{Principles of Parallel Programming, teaching assistant}{Spring 2015} \\
% \Event{Computational Thinking, in-class teaching assistant}{Fall 2013, Fall 2014}

% }





\begin{rSection}{Work Experience}

\begin{rSubSection}{Jones McClure Publishing}{Houston, Texas}
{Software Development Intern}{Summer 2013}
\item Created a mobile version of the O'Connor's Online platform.
\item Created administrative tools governing the behavior of the mobile site.
\end{rSubSection}

\end{rSection}





\iftoggle{cv}{\pagebreak}{}
\begin{rSection}{Personal Projects}

\begin{rSubSection}{YASP: Another Stats Page (\texttt{yasp.co})}{}
{Co-Founder, Software Developer, Public Relations}{Fall 2014 to present}
\item Developed new features, maintained existing codebase, and marketed \\
YASP: a free, volunteer-developed, open-source, project that provides \\
game- and player-specific statistics for the video game Dota 2.
\end{rSubSection}

\end{rSection}





\begin{rSection}{Hackathons}

\Event{HackRice (hosted by The Rice CS Club)}{Spring 2015, Spring 2016}

\end{rSection}




\begin{rSection}{Extracurricular Activities}

\iftoggle{cv}{

\begin{rSubSection}{The Rice Queer Resource Center (QRC)}{Houston, Texas}
{Co-Founder and President}{Fall 2014 to present}
\item Facilitated discussion among approximately twenty disparate committees.
\item Wrote a funding proposal to the Rice Undergraduate Student Association \\
to found the QRC and was approved by the student body to receive \$5,000.
\item Headed the Sexual Assault Committee, worked to update Ally Training, \\
worked to potentially hire a part-time staff person to support the QRC, \\
investigated founding a queer support group, and created the QRC's website.
\end{rSubSection}

\begin{rSubSection}{Out for Undergrad Technology Conference}{San Francisco, California}
{Student Participant}{25-27 September 2015}
\item Attended OUTC: a non-profit conference dedicated to helping \\ 
high-achieving LGBTQ undergraduates in technologically-relevant \\
STEM fields reach their full potential in their careers.
\end{rSubSection}}{

\Event{The Rice Queer Resource Center, Co-Founder and President}{Fall 2014 to present} \\
\Event{Out for Undergrad Technology Conference, participant}{25-27 September 2015} \\}
\Event{Academic Fellow and Mentor}{Fall 2014 to present} \\
\Event{Peer Academic Advisor}{Spring 2013 to present} \\
\Event{Rice Student Ambassador}{Spring 2013 to present}

\end{rSection}





\iftoggle{cv}{
\begin{rSection}{Awards and Honors}

\Event{Rice Alumni Pride Award}{Fall 2015} \\
\Event{President's Honor Roll}{Fall 2014, Fall 2015} \\
\Event{John and Harriet Millington Scholarship}{Fall 2014, Fall 2015} \\
\Event{Lon Wilson Service Award}{Spring 2015} \\
\Event{Genevieve Parkhill Lykes Scholarship}{Fall 2014} \\
\Event{Bracht-Verlander Scholarship}{Fall 2012} \\
\Event{National Merit Quarterfinalist}{Spring 2012} \\
\Event{AP Scholar with Honor}{Spring 2012} \\
\Event{National Honor Society}{2011 to 2012}

\end{rSection}
}{}





\iftoggle{cv}{\pagebreak
\begin{rSection}{Pertinent Coursework}

\Rice

\BeginUnivEvents
\Event{Advanced Topics in Object-Oriented Design}{Spring 2016} \\
\Event{Advanced Computer Game Creation}{Spring 2016} \\
\Event{Tools and Models for Data Science (A)}{Fall 2015} \\
\Event{Functional Programming (A)}{Fall 2015} \\
\Event{Operating Systems and Concurrent Programing (B)}{Spring 2015} \\
\Event{Introduction to Computer Security (A+)}{Spring 2015} \\
\Event{Reasoning about Algorithms (A)}{Fall 2014} \\
\Event{Compiler Construction (A-)}{Fall 2014} \\
\Event{Object-Oriented Design (A)}{Fall 2014} \\
\Event{Principles of Parallel Programming (B)}{Spring 2014} \\
\Event{Introduction to Computer Systems (A-)}{Spring 2014} \\
\Event{Introduction to Program Design (A)}{Fall 2013} \\
\Event{Algorithmic Thinking (A-)}{Spring 2013} \\
\Event{Fundamentals of Computer Engineering (B-)}{Spring 2013} \\
\Event{Computational Thinking (A)}{Fall 2012} \\
\Event{Introduction to Computational Engineering (A+)}{Fall 2012}
\EndUnivEvents

\end{rSection}}{}





\iftoggle{cv}{
\begin{rSection}{Standardized Test Scores}

\begin{rSubSection}{GRE}{November 2015}{}{}
\item Quantitative: \tab{$164/170$} \tab{(\nth{88} percentile)}
\item Verbal: \tab{} \tab{$161/170$} \tab{(\nth{87} percentile)}
\item Writing: \tab{} \tab{$4.5/6.0$} \tab{(\nth{80} percentile)}
\end{rSubSection}

\begin{rSubSection}{SAT}{October 2011}{}{}
\item Mathematics: \tab{$750/800$} \tab{(\nth{97} percentile)}
\item Reading: \tab{} \tab{$790/800$} \tab{(\nth{99} percentile)}
\item Writing: \tab{} \tab{$760/800$} \tab{(\nth{99} percentile)}
\end{rSubSection}

\end{rSection}}{}





\iftoggle{cv}{
\begin{rSection}{Miscellaneous Information}

Citizenship: USA

\end{rSection}}{}

\end{document}
